Literature Review

### 2018-12-30 Source/LiteratureReview/LiteratureReview.tex
added source

@@

@@

\date{2018-08-22}

@@

% IN THIS PARAGRAPH - CITE UK REPORT
Alzheimer's disease and other forms of dementia are affecting a significant proportion of geriatric population in the world today. According to a recent report commissioned by the Alzheimer's Society in 2015, they estimate the prevalence of AD in the UK at approximately 815,000 people. This represents 1 in 14 of those aged 65 or over and 1 in 79 of the general population. From a financial perspective, they estimate an annual spend of £4.3 billion of which approximately £85 million is spent solely on diagnosis and that the total impact of AD (excluding the costs associated with early onset dementia) is £26.3 billion annually. Globally, this picture is a lot bleaker. Another report by Alzheimer's Disease International suggests that in 2015 there were 46 million people with a diagnosis of AD and that number is expected to hit 131.5 million by 2050 \cite{Prince2015}. The report also states that the worldwide cost of AD in 2018 is estimated to be in the region of one trillon US dollars.\newline

@@

Alzheimer's Disease (AD) is a neurodegenerative disease in which, from a physiological perspective, the brain develops neurofibrillary tangles and neuritic plaques along with the deterioration and loss of cortical neurons and synapses. However, a definitive diagnosis of Dementia can only produced at post-mortem. From a clinical psychology perspective, those who have dementia have cognitive deficits such as problems with episodic and semantic memory, organising and planning, difficulties with language and visuospatial deficits\cite{AmericanPsychiatricAssociation2013}. In addition, these symptoms are often accompanied by emotional difficulties such as depression and irritability and behavioural difficulties.  \newline

@@

Current thinking suggests that the cognitive deficits associated with AD often begin before the clinical symptoms of the disease become apparent. Researchers propose that neurofibrillary tangles and other associated physiological effects of AD develop over time and alter cognitive function until a threshold is reached and clinical symptoms become more obvious. \cite{Nestor2006}. The case of Iris Murdoch illustrates this theory well. Le et al \cite{Le2012}found, in their analysis of three writers and the novels they wrote, that Iris Murdoch's work declined subtly over time, but there was a steep drop off in the use of language in her last novel. If this theory holds true more generally, it should be possible to detect subtle cognitive changes in language and memory before a clinical diagnosis can be formed.\newline 

@@

One of the most common ways in which clinicians traditionally make an early diagnosis of cognitive impairment is through the use of the Mini Mental State Examination (MMSE) \cite{Folstein1975}. The MMSE is a brief questionnaire consisting of eleven questions which tests cognitive aspects of mental function and requires only 5-10 minutes to administer \cite{Folstein1975}. The MMSE is chosen due to it's effectiveness at assessing a person's cognitive mental state at a specific point in time, as well as being as sensitive to changes as a more detailed and complex assessment such as the Wechler Adult Intelligence Scale \cite{Folstein1975}. Whilst the MMSE is useful as a brief screening tool it has it's limitations. The MMSE was not specifically created to screen for dementias and therefore does not interrogate key aspects of cognitive impairment known to be affected in dementia. It also has limited value in assessing under educated subjects and a meta-analysis on the effectiveness of the MMSE as a diagnostic tool for dementia to showed that it's accuracy was low (sensitivity between 78.4\% and 85.1\% and specificity between 81.3\% and 87.8\%) \newline 
% Need to cite Should the Mini-Mental State Examination be retired above.

@@

As the MMSE is shown to have low accuracy specifically in the diagnosis of dementia, it becomes necessary for professionals to employ the use of other tools or measures such as the Free Cued Selective Reminding Test (FCSRT) or the Montreal Cognitive Assessment. These tests have the benefits of being much more accurate at diagnosing cognitive impairment and discriminating between dementia and other types of cognitive impairment at the cost time and training of psychological professionals such as clinical psychologists in administering these tests. Given the burden on these professionals is likely to increase due to a growing elderly population or in the case of developing countries where the clinician / patient ratio is already unsustainable, it seems useful to find less burdensome ways do aid professionals in diagnosing dementia. \newline

@@

The two main ways in which diagnosis is performed is through assessment of memory and language. Tests of memory are classically among the most accurate ways of diagnosing dementia, however they suffer from the same reliance on clinicians to administer these tests in a clinical setting. Language however is a lot easier to collect and can be done in more naturalistic settings. As with memory, these tests can be done over time and would be able to chart a patients language degeneration over time. Given that language is less intrusive to test and requires a lot of the cognitive processes that may be impacted by AD, a lot of research has focused on measure decline in the use of language in those with AD.  \newline

@@

There are a wide number of factors that are involved in language degeneration in the elderly, and consequently there will be an expected amount of variability between subjects. The consensus is that this decline is typically accelerated by the presence of dementia \cite{Berisha2015}. Given this statement, it seems logical to conclude that one of the key variables that distinguishes language decline in healthy individuals vs those with dementia is the rate of change in which the decline occurs. \newline

@@

According to the DSM 5 \cite{AmericanPsychiatricAssociation2013}, those with Mild dementia suffer from noticeable word finding difficulty. They may substitute general terms for more specific terms and may avoid the use of specific names of acquaintances. There may be grammatical errors involving subtle omission or incorrect use of articles, prepositions, auxiliary verbs, etc. Those who have progressed from Mild to Major depression also have difficulties with expressive or receptive language. They will often use general-use phrases such as "that thing" and "you know what I mean" and prefers general pronouns rather than names. With severe impairment, sufferers may not even recall names of closer friends and family. Idiosyncratic word usage, grammatical errors, and spontaneity of output and economy of utterances occur. Echolalia (meaningless repetition of another person's spoken words) and automatic speech typically precede mutism. With the wide range of deficits someone with AD can suffer, it makes sense to try to categorise these deficits in some way.\newline
One of the most famous pieces of research on the topic of language decline in dementia was by Berisha and Liss (2015) \cite{Berisha2015} who examined speeches and public interviews of former US president Ronald Reagan. They found that Reagan's speeches towards the end of his presidency suffered from difficulties in word-finding, inappropriate phrases and uncorrected sentences which are hallmarks of language deterioration associated with Alzheimer's Disease. It turned out later to be the case that he had Alzheimer's Disease. Another classical study by Snowdon et al (1996) \cite{Snowdon1996} looked at whether linguistic ability in early life was associated with cognitive function and AD in later life. They found that idea density (defined as the number of expressed propositions divided by the number of words) was a key predictor in predicting whether nuns would go on to develop AD in later life. They found that those who would go on to develop AD all had low idea density in early life and they found no AD present in those with high idea density in early life. As we can see, just with these two pieces of research the range of language deficits in those who suffer with AD are wide and varied and differ as the disease progresses. \newline

@@

@@

Given the relative strengths of the Narrative description task vs Picture description task, there are few pieces of research research that have used Machine Learning to analyse features from Narrative picture tasks \cite{Fraser2014}. This could be down to the availability of data and the absence of any meaningful sets of transcripts of participants performing this task. However, this could be an interesting direction to take research in the future to see if features generated from this task could be used to predict MCI or AD.  \newline

@@

Interviews can also be used to elicit language, the idea of employing questions to guide a conversation between speakers. There are three types of interviews: unstructured, structured and semi-structured. Structured interviews tend to produce very limited speech and therefore has never been used in this area \cite{Boschi2017}. Unstructured interviews are open ended and generally do not conform to any particular pattern. They use generic themes such as family or hobbies to guide the conversation. Whilst this is the most ecologically valid form of conversation and therefore language generation, it's unstructured nature means that the protocol cannot be consistent and therefore reproduced. Semi-structured interviews are therefore preferred other forms of interview as a middle ground. The semi structured nature of these interviews means that there is some replicability but does not constrain the participant in answering questions. \newline

@@

The analysis of interviews can be difficult to analyse as both the content can vary even between participants. It is also difficult to measure as there are no pre-defined task goals in comparison to the other two methods. Nevertheless, this is the most naturalistic setting for looking at language production and can be used to look at the syntactic and semantic parts of language generation \cite{Sajjadi2012}. There have been some attempts to use interviews to to assess language production in AD with promising results \cite{Asgari2017, Guinn2015}.\newline

@@

@@

When navigating the English language it is necessary to distinguish between what a sentence says in both semantic and pragmatic terms. Semantic meaning refers to the meaning of the words in a sentence local only to the given sentence. Another way to put this is, semantics considers the meaning of words without taking into account the context in which these words are spoken. Pragmatic meaning refers looks at the same sentence in terms of words and grammar but takes into account the situation or context in which these words are spoken. \newline

@@

Another approach to linguistic analysis in this field is the idea of measuring semantic content and complexity. According to Emery (2000) \cite{Emery2000} in which she states that Semantic and Syntactic skills deteriorate first in people with MCI and AD. If this is true, then psychological measures of semantic and syntactic skills should be able to pick up signs of deterioration and act as markers for possible MCI and AD. An example of these measures is the concept of idea density. Formally, idea density is defined as the average number of propositions per sentence \cite{Kintsch1973} and this was used to successfully differentiate between people who would later go on to develop AD \cite{Snowdon1996}. Type to Token Ratio, Brunet's Index and Honore's Statistic are two more examples of validated measures which are used to measure the lexical diversity of a given piece of text. This has also shown to be effective in differentiating between MCI, AD and Controls, with those with language impairments \cite{Bucks2000} and this has carried through in research involving machine learning \cite{Wang2016, Thomas2005}.  \newline

@@

@@

One study examined verbal preservation in the description of Norman Rockwell prints, dividing the total number of words within perseverations by total number of words in the speech sample. The authors also calculated rate of perseveration on two other language tasks: confrontation naming and generative naming. Across all tasks, the AD group produced significantly more perseverations than controls; however, on the picture description task alone, there were no significant differences between the two groups. The authors theorised that this was because picture description was an easier taks because there was the visual stimulus, similar to the arguement made by Bschor et al. \newline 

@@

There are a number of studies, that have examined "melodic line", which is a subjective measure of speech prosody defined as "the appropriate use of intonational contour, including alterations in pitch, volume and duration". For instance, Forbes-McKay compared melocdic line using a "simple" picuture such as the Cookie Theft picture vs a complex picture. The number of pictorial themes differentiated the simple tasks from the complex. Results showed no group differences on simple picture tasks (Cookie Theft and Tripping Woman) but there were differences in melodic line for the complex picture tasks. Fraser et al examined several acoustic features of speech in patients with AD ussing machine learning methods that captureed both rate and phonation patterns, and found acoustic abnormalities to be a significant factor. Konig et al, also used an automated feature analysis examining vocal and temporal aspects of speech among controls, and patients with MCI or AD, and reported a classification of 81%.

@@

\section{State of literature into Natural Language processing techniques}
As we can see, diagnosing dementia through analysis has a large background in terms of psychological research. However, a lot of more current research has called for the use of machine learning as a way of assisting in the process of diagnosis \cite{Boschi2017}.

%% IS THERE ANY RESEARCH ON THIS?

%Current state-of-the-art diagnostic measures of AD are
%invasive (CSF analysis), expensive (neuroimaging), and
%time-consuming (neuropsychological assessment). Furthermore,
%these measures are limited to specialty clinics and
%thus have limited accessibility as high-throughput, or frontline,
%screening and diagnostic tools for AD. More importantly,
%nonspecialists are often inaccurate at identifying
%early AD and MCI [5]. Thus, there is an increasing need
%for additional noninvasive and/or cost-effective tools, allowing
%frontline identification of subjects in the preclinical or
%early clinical stages of AD who could be suitable for monitoring
%in specialty clinics and for early treatment. Implementation
%of effective screening instruments will allow diagnosis
%earlier in the course of dementia, even at the point when
%memory function is still essentially within the normal range.
%This strategy would enable an earlier, and potentially more
%effective, prevention and treatment of AD with a special
%focus to preserve cognitive functions

\section{Conclusions and Future Work}
It appears that both frequency based approaches and approaches that use measures of linguistic complexity have both been shown to be effective in various experimental settings. The fact that there are two vastly different perspectives to tackling this question, and even within these perspectives there are a range of various methodologies leaves the field with a sense of confusion as to the most effective way to solving the problem. \newline
\par
Identification of language impairment is key idea in the diagnosis of AD and early diagnosis can alter the prognosis and change the management of this degenerative disorder as well as provide new opportunities to study the progression of the disease. Given the burden on the diagnosis of AD on professionals there has been a call to use technology to potentially ease this burden \cite{Boschi2017}. It has already been shown that analysis of speech and language has shown markers that pre-date the official diagnosis of dementia \cite{Snowdon1996, Berisha2015}. A significant amount of research has gone into the use of machine learning techniques to potentially look at the automated classification of participants with MCI and/or AD, however this is a new area of research and there are some gaps in our knowledge. \newline 
\par
One of the areas for research to study is a careful examination of the features that are being used to measure language deterioration. For example, Zimmerer (2016) \cite{Zimmerer2016} describes connectivity in such as a way that correlates directly with what Mueller (2018) \cite{Mueller2018a} calls Fluency. Whilst these are very nuanced measures which differ slightly in the form they take, the sheer range of measures and features being produced make it difficult to conceptualise as part of the larger problem. Some work needs to be done in producing a consistent list of measures that are validated using existing datasets and can be used for future research moving forward. \newline
\par
\subsection{Future Work}
Future research should also be directed towards developing non-intrusive ways of detecting subtle changes in language based in the home, such that any deterioration that could indicate the presence of MCI or AD and be flagged up early in the progression of any potential cogntive impairment for further review via referral. Machine learning approaches seem to be the most logical approach for achieving this aim. Further, despite the quality of datasets being used to 'backtest' these algorithms, further research should look at generating additional datasets to increase the validity of the results found so far as well as using other methods to generate data other than Picture Description tasks which we could claim are limited in scope. \newline
\par
The recent resurgence in the use of neural networks and deep learning is because of it's significantly improved performance on many problems and it's ability to scale from small to large datasets. Another key benefit of deep learning is it's ability to automate the process of feature engineering. Feature engineering, with this particular problem is an interesting debate as there are currently numerous ways in which to try to generate features. \newline
\par 
This area of research is extremely promising in its early results and the impact of successful research would be life changing for both individuals and the health of the worlds aging population in general. \newline

>>>>

%% TO DO LIST
% Fix the table on the literature search.
% Talk about measures of lexical diversity (TTR, Brunets, Honore's)

@@

\usepackage{graphicx}
\usepackage{float}

@@

\date{2018-09-05}

@@

Alzheimer's disease (AD) and other forms of dementia affect a significant proportion of the geriatric population in the world today and is currently the sixth leading cause of death in the US and the leading killer of women in the UK. According to a recent report commissioned by the Alzheimer's Society in 2015, they estimate the prevalence of AD in the UK at approximately 815,000 people. This represents 1 in 14 of those aged 65 or over and 1 in 79 of the general population \cite{Sturrock2016}. From a financial perspective, they estimate an annual spend of £4.3 billion of which approximately £85 million is spent solely on diagnosis and that the total impact of AD (excluding the costs associated with early onset dementia) is £26.3 billion annually. Globally, this picture is a lot bleaker. Another report by Alzheimer's Disease International suggests that in 2015 there were 46 million people with a diagnosis of dementia globally and that number is expected to hit 131.5 million by 2050 \cite{Prince2015}. The report also states that the worldwide cost of AD in 2018 is estimated to be in the region of one trillon US dollars. \newline

@@

% In this paragraph, look for the study which actually has these figures.
Despite this growing problem, at present there are no drugs that improve the prognosis of those suffering with AD. All the drugs that are on the market are designed to manage symptoms. Whilst there are numerous investigational drugs in development for the treatment of AD, a larger than normal percentage (99.6\%) of these drugs fail in clinical trials (in contrast to anti-cancer drugs which have a 80\% failure rate) \cite{Alzheimer2016}. Researchers have proposed that a possible reason for the lack of success is that the drugs treatments are initiated too far along in the progression of the disease and thus much of the degeneration of the brain has already taken place.  \newline

@@

Alzheimer's Disease is a neurodegenerative disease in which, from a physiological perspective, the brain develops neurofibrillary tangles and neuritic plaques along with the deterioration and loss of cortical neurons and synapses. Whilst a definitive diagnosis of Dementia can only produced at post-mortem, there are a number of clinical indicators from psychological perspective that can indicate that dementia is present. From a clinical psychology perspective, those who have dementia have cognitive deficits such as problems with episodic and semantic memory, organising and planning, difficulties with language and visuospatial deficits\cite{AmericanPsychiatricAssociation2013}. In addition, these symptoms are often accompanied by emotional difficulties such as depression and irritability and behavioural difficulties. \newline

@@

Current thinking suggests that the cognitive deficits associated with AD often begin before the clinical symptoms of the disease become apparent. Researchers propose that neurofibrillary tangles and other associated physiological effects of AD develop over time and alter cognitive function until a threshold is reached and clinical symptoms become more obvious \cite{Nestor2006}. The case of Iris Murdoch illustrates this theory well. Le et al \cite{Le2012}found, in their analysis of three writers and the novels they wrote, that Iris Murdoch's work declined subtly over time, but there was a steep drop off in the use of language in her last novel. If this theory holds true more generally, it should be possible to detect subtle cognitive changes in language and memory before a clinical diagnosis can be formed. However, one of the challenges of this approach is differentiating natural cognitive decline due to aging with decline due to a form of dementia.\newline 

@@

One of the most common ways in which clinicians traditionally make an early diagnosis of cognitive impairment is through the use of the Mini Mental State Examination (MMSE) \cite{Folstein1975}. The MMSE is a brief questionnaire consisting of eleven questions which tests cognitive aspects of mental function and requires only 5-10 minutes to administer \cite{Folstein1975}. The MMSE is chosen due to it's effectiveness at assessing a person's cognitive mental state at a specific point in time, as well as being as sensitive to changes as a more detailed and complex assessment such as the Wechler Adult Intelligence Scale \cite{Folstein1975}. Whilst the MMSE is useful as a brief screening tool it has it's limitations. The MMSE was not specifically created to screen for dementias and therefore does not interrogate key aspects of cognitive impairment known to be affected in dementia. It also has limited value in assessing under-educated subjects and a meta-analysis on the effectiveness of the MMSE as a diagnostic tool for dementia to showed that it's accuracy was low (sensitivity between 78.4\% and 85.1\% and specificity between 81.3\% and 87.8\%). As the MMSE is shown to have low accuracy specifically in the diagnosis of dementia, it becomes necessary for professionals to employ the use of other tools or measures such as the Free Cued Selective Reminding Test (FCSRT) or the Montreal Cognitive Assessment (MoCA). These tests have the benefits of being much more accurate at diagnosing cognitive impairment and discriminating between dementia and other types of cognitive impairment at the cost time and training of psychological professionals such as clinical psychologists in administering these tests. Given the burden on these professionals is likely to increase due to a growing elderly population or in the case of developing countries where the clinician / patient ratio is already unsustainable, it seems useful to find less burdensome ways to aid professionals in diagnosing dementia. \newline

@@

The two main ways in which diagnosis is performed is through assessment of memory and language. Tests of memory are classically among the most accurate ways of diagnosing dementia, however these tests suffer from the same reliance on trained clinicians to administer these tests in a clinical setting. Language however is a lot easier to collect and can be done in more naturalistic settings. As with memory, these tests can be done over time and would be able to chart a patients language degeneration over time. Given that language is less intrusive to test and requires a lot of the cognitive processes that may be impacted by AD, a lot of research has focused on measure decline in the use of language in those with AD. There are a wide number of factors that are involved in language degeneration in the elderly, and consequently there will be an expected amount of variability between subjects. The consensus is that this language degeneration is typically accelerated by the presence of dementia \cite{Berisha2015} and that a potential indicator of dementia is the rate of change in which the decline occurs relative to a fixed point in time rather than a comparison across a cohort of individuals. \newline

@@

According to the DSM 5 \cite{AmericanPsychiatricAssociation2013}, those with mild dementia suffer from noticeable word finding difficulty. They may substitute general terms for more specific terms and may avoid the use of specific names of acquaintances. There may be grammatical errors involving subtle omission or incorrect use of articles, prepositions, auxiliary verbs, etc. Those who have progressed from Mild to Major depression also have difficulties with expressive or receptive language. They will often use general-use phrases such as "that thing" and "you know what I mean" and prefers general pronouns rather than names. With severe impairment, sufferers may not even recall names of closer friends and family. Idiosyncratic word usage, grammatical errors, and spontaneity of output and economy of utterances occur. Echolalia (meaningless repetition of another person's spoken words) and automatic speech typically precede mutism. With the wide range of deficits someone with AD can suffer, it makes sense to try to categorise these deficits in some way.\newline

@@

One of the most famous pieces of research on the topic of language decline in dementia was by Berisha and Liss (2015) \cite{Berisha2015} who examined speeches and public interviews of former US president Ronald Reagan. They found that Reagan's speeches towards the end of his presidency suffered from difficulties in word-finding, inappropriate phrases and uncorrected sentences which are hallmarks of language deterioration associated with Alzheimer's Disease. It turned out later to be the case that he had Alzheimer's Disease. Another classical study by Snowdon et al (1996) \cite{Snowdon1996} looked at whether linguistic ability in early life was associated with cognitive function and AD in later life. They found that idea density (defined as the number of expressed propositions divided by the number of words) was a key predictor in predicting whether nuns would go on to develop AD in later life. They found that those who would go on to develop AD all had low idea density in early life and they found no AD present in those with high idea density in early life. As we can see, just with these two pieces of research the range of language deficits in those who suffer with AD are extremely variable and can differ from patient to patient as the disease progresses. \newline

@@

\begin{figure}[H]
\centering 
\includegraphics[width=240px, height=150px]{BCTPicture.png}
\caption{Cookie Theft Picture.\label{white}}
\end{figure}

@@

Given the relative strengths of the Narrative description task vs Picture description task, there are few pieces of research  that have used Machine Learning to analyse features from Narrative picture tasks \cite{Fraser2014}. This could be due to the availability of data and the absence of any meaningful sets of transcripts of participants performing this task. However, this could be an interesting direction to take research in the future to see if features generated from this task could be used to predict MCI or AD.  \newline

@@

Interviews can also be used to elicit language in a more natural way by asking questions to guide a conversation between speakers. There are three types of interviews: unstructured, structured and semi-structured. Structured interviews tend to produce very limited speech and therefore has never been used in this area \cite{Boschi2017}. Unstructured interviews are open ended and generally do not conform to any particular pattern. They use generic themes such as family or hobbies to guide the conversation. Whilst this is the most ecologically valid form of conversation and therefore language generation, it's unstructured nature means that the protocol cannot be consistent and therefore reproduced. Semi-structured interviews are therefore preferred over other forms of interview as a middle ground. The semi structured nature of these interviews means that there is some replicability but does not constrain the participant in answering questions. \newline

@@

The analysis of interviews can be difficult to analyse as both the content can vary even between participants. It is also difficult to measure as there are no pre-defined task goals in comparison to the other two methods. Nevertheless, this is the most naturalistic setting for looking at language production and can be used to look at the syntactic and semantic parts of language generation \cite{Sajjadi2012}. There have been some attempts to use interviews to assess language production in AD with promising results \cite{Asgari2017, Guinn2015 .\newline

@@

Single word tasks such as the Boston Naming Test and other such standardized language tests generally target a participants verbal fluency where this is defined as the ability to form and express words in accordance with certain criteria. For example, a common test of verbal fluency would be to ask a participant to name as many words in a given category in a limited time frame. These categories can be objects such as animals or sports, or can be words beginning with a specific letter. There are a number of benefits to using single word tasks. From a research methodology perspective, using a standardized test allows researchers to target a very specific process in language generation and isolate factors that impact performance in language well. However, this approach does not take into account the symbiotic nature of language processes. \newline
Connected language tasks, such as the picture description task and interviews described above are a much more reflective of processes involved in natural language generation. They are able to be relatively constrained in the language available to be used, for example in the picture description task, or they can be unconstrained in the form of interviews. \newline

@@

When navigating the English language it is necessary to distinguish between what a sentence says in both semantic and pragmatic terms. Semantic meaning refers to the meaning of the words in a sentence local only to the given sentence. Another way to put this is, semantics considers the meaning of words without taking into account the context in which these words are spoken. Pragmatic meaning refers looks at the same sentence in terms of words and grammar but takes into account the situation or context in which these words are spoken. Emery in her literature review looks at all levels of language tasks except for pragmatics, however   \newline

@@

Another approach to linguistic analysis in this field is the idea of measuring semantic content and complexity. According to Emery (2000) \cite{Emery2000} in which she states that Semantic and Syntactic skills deteriorate first in people with MCI and AD. If this is true, then psychological measures of semantic and syntactic skills should be able to pick up signs of deterioration and act as markers for possible MCI and AD. An example of a semantic complexity measure is the concept of idea density. Formally, idea density is defined as the average number of propositions per sentence \cite{Kintsch1973} and this was used to successfully differentiate between people who would later go on to develop AD \cite{Snowdon1996}. Some examples of semantic content measures are Type to Token Ratio, Brunet's Index and Honore's Statistic  which are used to measure the lexical diversity of a given piece of text and/or utterance.  This has also shown to be effective in differentiating between MCI, AD and Controls, with those with language impairments \cite{Bucks2000} and this has carried through in research involving machine learning \cite{Wang2016, Thomas2005}.  \newline

@@

\begin{figure}[H]
\centering
\includegraphics[width=240px, height=150px]{picnic-scene.jpg}
\caption{Picnic Scene taken from the Western Aphasia Battery (WAB).\label{white}}
\end{figure}

@@

One study examined verbal preservation in the description of Norman Rockwell prints, dividing the total number of words within perseverations by total number of words in the speech sample. The authors also calculated rate of perseveration on two other language tasks: confrontation naming and generative naming. Across all tasks, the AD group produced significantly more perseverations than controls; however, on the picture description task alone, there were no significant differences between the two groups. The authors theorised that this was because picture description was an easier taks because there was the visual stimulus, similar to the argument made by Bschor et al. \newline 

@@

There are a number of studies, that have examined "melodic line", which is a subjective measure of speech prosody defined as "the appropriate use of intonational contour, including alterations in pitch, volume and duration". For instance, Forbes-McKay compared melocdic line using a "simple" picuture such as the Cookie Theft picture vs a complex picture. The number of pictorial themes differentiated the simple tasks from the complex. Results showed no group differences on simple picture tasks (Cookie Theft and Tripping Woman) but there were differences in melodic line for the complex picture tasks. Fraser et al examined several acoustic features of speech in patients with AD ussing machine learning methods that captureed both rate and phonation patterns, and found acoustic abnormalities to be a significant factor. Konig et al, also used an automated feature analysis examining vocal and temporal aspects of speech among controls, and patients with MCI or AD, and reported a classification of 81\%.

@@

\section{State of literature into Natural Language processing techniques}
As we can see, diagnosing dementia through analysis has a large background in terms of psychological research. However, a lot of more current research has called for the use of machine learning as a way of assisting in the process of diagnosis \cite{Boschi2017}. Generally speaking, Natural Language Processing (NLP) systems mimic the semiotic perspective on language. That is to say that we can subdivide NLP processes into different components. This broadly fits with the literature review conducted by Emery.
\begin{enumerate}
	\item Morphological/Lexical: providing the basic language elements or vocabulary, such as words, their roots and inflections.
	\item Syntactic: for grouping and sequencing elementds within samples of language (usually sentences).
	\item Semantic: for knowing the meaning of an utterance, usually defined in terms of the 'truth value' of the logical propositions that are thought to be expressed by sentences.
	\item Pragmatic: for understanding the context and purpose of an utterance.
\end{enumerate}
\subsection{Traditional methods of Machine Learning and Natural Language Processing}

\subsection{Deep Learning}

\section{The problems with attempting early diagnosis of dementia and the ethics of actively screening for it}
It is challenging to characterise Dementia as a disease as it's more syndrome. The clinical features that combine to meet the diagnostic criteria for Dementia or it's variants are continuous in nature and also impacted by other variables. For example, cognitive performance is affected by previous education and ability to live independently is impacted by a person's physical health. Also, the individual who may develop symptoms that indicate the onset of dementia needs the insight to recognise them, or family members will need to do so and also deduce that there is value to admitting there is a problem and seeking help before the deterioration is too great. \newline
To detect dementia early requires an understanding of how this presents early in it's progression, but as described above there are a number of potential ways in which individuals with dementia could be impacted but no consistent list of criteria has been produced. Even for AD, the most prevalent form of dementia, clinical diagnosis can only be confirmed after death through autopsy. In addition, population studies have shown that people over the age of 80 show similar changes in the brain in those that do not have dementia. Therefore, it's difficult to say with certainty that any symptoms can definitely cause dementia despite the fact that these symptoms are commonly present in those that have dementia. \newline
\section{Conclusions and Future Work}
It appears that there are a number of approaches that have been shown to be effective in various experimental settings. The fact that there are a numerous array of different perspectives to tackling this question, and even within these perspectives there are a range of various methodologies leaves the field with a sense of confusion as to the most effective way to solving the problem. \newline
Current state-of-the-art diagnostic measures of AD are invasive (CSF analysis), expensive (neuroimaging), and time-consuming (neuropsychological assessment). Furthermore, these measures are limited to specialty clinics and thus have limited accessibility as high-throughput, or frontline, screening and diagnostic tools for AD. More importantly, nonspecialists are often inaccurate at identifying early AD and MCI [5]. Thus, there is an increasing need for additional noninvasive and/or cost-effective tools, allowing frontline identification of subjects in the preclinical or early clinical stages of AD who could be suitable for monitoring in specialty clinics and for early treatment. Implementation of effective screening instruments will allow diagnosis earlier in the course of dementia, even at the point when memory function is still essentially within the normal range. This strategy would enable an earlier, and potentially more effective, prevention and treatment of AD with a special focus to preserve cognitive functions \newline
Identification of language impairment is key idea in the diagnosis of AD and early diagnosis can alter the prognosis and change the management of this degenerative disorder as well as provide new opportunities to study the progression of the disease. Given the burden on the diagnosis of AD on professionals there has been a call to use technology to potentially ease this burden \cite{Boschi2017}. It has already been shown that analysis of speech and language has shown markers that pre-date the official diagnosis of dementia \cite{Snowdon1996, Berisha2015}. A significant amount of research has gone into the use of machine learning techniques to potentially look at the automated classification of participants with MCI and/or AD, however this is a new area of research and there are some gaps in our knowledge. \newline 
One of the areas for research to study is a careful examination of the features that are being used to measure language deterioration. For example, Zimmerer (2016) \cite{Zimmerer2016} describes connectivity in such as a way that correlates directly with what Mueller (2018) \cite{Mueller2018a} calls Fluency. Whilst these are very nuanced measures which differ slightly in the form they take, the sheer range of measures and features being produced make it difficult to conceptualise as part of the larger problem. Some work needs to be done in producing a consistent list of measures that are validated using existing datasets and can be used for future research moving forward. \newline
\subsection{Future Work}
Future research should also be directed towards developing non-intrusive ways of detecting subtle changes in language based in the home, such that any deterioration that could indicate the presence of MCI or AD and be flagged up early in the progression of any potential cogntive impairment for further review via referral. Machine learning approaches seem to be the most logical approach for achieving this aim. Further, despite the quality of datasets being used to 'backtest' these algorithms, further research should look at generating additional datasets to increase the validity of the results found so far as well as using other methods to generate data other than Picture Description tasks which we could claim are limited in scope. \newline
The recent resurgence in the use of neural networks and deep learning is because of it's significantly improved performance on many problems and it's ability to scale from small to large datasets. Another key benefit of deep learning is it's ability to automate the process of feature engineering. Feature engineering, with this particular problem is an interesting debate as there are currently numerous ways in which to try to generate features as I have described above.\newline
This area of research is extremely promising in its early results and the impact of successful research would be life changing for both individuals and the health of the worlds aging population in general. \newline
